Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2016-01-21 paper.tex
Put a and b labels on exp setup figure
Clean up ADV positioning paragraph

% Add packages and commands to include here
% The amsmath, amsthm, amssymb, hyperref, caption, float and color packages are
% loaded by the MDPI class.
\usepackage{graphicx}
%\usepackage{subfigure,psfig}
\usepackage[draft]{todonotes}
\usepackage{lineno}
\usepackage[utf8]{inputenc}
\usepackage{booktabs} 
\usepackage{multirow}
\usepackage{soul}
\usepackage{microtype}
\def \p{\partial}
\def \d{\mathrm{d}}
\def \D{\mathrm{D}}
\setitemize{parsep=6pt,itemsep=0pt,leftmargin=*,labelsep=5mm}
\setenumerate{parsep=6pt,itemsep=0pt,leftmargin=*,labelsep=5mm}
\setlist[description]{itemsep=0mm}

@@

 \includegraphics[width=0.7\textwidth]{figures/exp-setup-photo}

 \includegraphics[width=0.7\textwidth]{figures/exp_setup_drawing}

 \caption{\hl {Experimental} setup: turbine test bed installed in the UNH tow tank.}
 %please mark (a) and (b) in the figure and label (a) and (b) in the figure caption.

@@

Each wake map was generated by positioning a Nortek Vectrino+ acoustic Doppler
Velocimeter (ADV), measuring three components of velocity at a 200-Hz sampling
frequency, at 270 different locations, varied in the cross-stream and vertical
directions at one turbine diameter downstream ($x/D=1$). These locations have
vertical coordinates from the turbine centerline up to $z/H=0.625$, ranging in
the cross-stream direction $y/R = \pm 3$. These locations are shown in
Figure~\ref{fig:wake-locations}.

>>>>

% Add packages and commands to include here
% The amsmath, amsthm, amssymb, hyperref, caption, float and color packages are
% loaded by the MDPI class.
\usepackage{graphicx}
%\usepackage{subfigure,psfig}
\usepackage[draft]{todonotes}
\usepackage{lineno}
\usepackage[utf8]{inputenc}
\usepackage{booktabs} 
\usepackage{multirow}
\usepackage{soul}
\usepackage{microtype}
\usepackage{caption}
\usepackage{subcaption}
\def \p{\partial}
\def \d{\mathrm{d}}
\def \D{\mathrm{D}}
\setitemize{parsep=6pt,itemsep=0pt,leftmargin=*,labelsep=5mm}
\setenumerate{parsep=6pt,itemsep=0pt,leftmargin=*,labelsep=5mm}
\setlist[description]{itemsep=0mm}

@@

\begin{figure}[H]
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=0.7\textwidth]{figures/exp-setup-photo}
        \caption{}
        \label{fig:exp-setup-photo}
    \end{subfigure}

    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=0.7\textwidth]{figures/exp_setup_drawing}
        \caption{}
        \label{fig:exp-setup-dwg}
    \end{subfigure}

    \caption{Experimental setup photo (a) and drawing (b): turbine test bed
        installed in the UNH tow tank.}

@@

Each wake map was generated by positioning the ADV, which measured three
components of velocity at a 200 Hz sampling frequency, at 270 different
locations, varied in the cross-stream and vertical directions at one turbine
diameter downstream ($x/D=1$). These locations had vertical coordinates from the
turbine centerline up to $z/H=0.625$, ranging in the cross-stream direction $y/R
= \pm 3$. These locations are shown in Figure~\ref{fig:wake-locations}.
